Gammapy: A Python package for gamma-ray astronomy

### 2023-01-09 src/ms-review.tex
implement cosimo comments
Signed-off-by: Atreyee Sinha <asinha@ucm.es>

	{Context} In the last two decades the measurement of \gammaray emission from the universe has
	evolved from a niche area of closed collaborations operating with proprietary data and software into
	an active and exciting field of astrophysics. The next generation of \gammaray instruments,
	such as the Cherenkov Telescope Array (CTA), will be operated as open observatories with publicly available
	data, which will require open high-level astronomy software customised for high energy astrophysics.

	{Aims} In this article, we present the first the Long-term Support (LTS) release of \gammapy v1.0. \gammapy
	is a community-developed, open-source Python package for \gammaray astronomy. Integrated into the general
	python eco-system, it is built on Numpy, Scipy and Astropy and uses open FITS based data formats for serialisation.
	It provides a uniform platform for reduction and modelling of data from many \gammaray instruments.

	{Methods} Starting from event list and instrument response functions at the so called "Data Level 3",
	\gammapy provides pipelines for reduction of the input data to binned WCS, HEALPix or region based data structures.
	A variety of background reduction methods, including traditional techniques like the Reflected and Ring regions,
	as well as novel 3D Field of View Likelihood techniques, are supported. The binned data can then be modelled
	using Poisson maximum likelihood fitting. While a variety of in-built spectral, temporal and spatial models
	are supplied, it also supports implementation of custom user defined models. Estimation of flux points, likelihood
	profiles and light curves are also implemented.

	{Results} The flexible API allows a joint likelihood analysis between different datasets,
	thus providing a simple platform for handling time dependent instrument responses,
	different events classes, or combining data from multiple separate instruments. The results are continuously
	validated with previously published ones. We show analysis examples using open data from various observatories: \fermi., \hess , MAGIC, CTA (simulated),
	and HAWC. 
}

>>>>

	{Context} Traditionally, the \gammaray universe has been probed
	 by small collaborations of scientists employing proprietary data and analysis software.
	 However, the next generation of \gammaray instruments,
	 such as the the Cherenkov Telescope Array (CTA), will be operated as open observatories.
	 Alongside the data, the observatories will make available to the astronomical community
	 software tools for their analysis. This necessity prompted the development, in the last decade,
	 of open high-level astronomy software customised for high energy astrophysics.

	{Aims} In this article, we present \gammapy, an open-source python package for the analysis of \gammaray data,
	and illustrate the functionalities of the first long-term release of the software, version 1.0.
	Built on the modern python scientific ecosystem, \gammapy provides a uniform platform for reducing and
	modelling data from different gamma-ray instruments. \gammapy complies with several well-established
	data conventions in high-energy astrophysics, providing serialised data products that are interoperable
	with other software.

	{Methods} Starting from event list and instrument response functions at the so called "Data Level 3",
	\gammapy provides pipelines for creating reduced data binned in energy and coordinates.
	To facilitate the rejection of the hadronic background, several techniques for background estimation
	 are implemented in the package.
	 After the data are binned, the flux and morphology of one or more \gammaray sources can be estimated
	 using Poisson maximum likelihood fitting
	 and assuming a variety of spectral, temporal, and spatial models.
	  Estimation of flux points, likelihood profiles and light curves are also implemented.

	{Results} After describing the structure of the package, we demonstrate the capabilities of \gammapy
	performing several traditional analyses in gamma-ray astronomy with publicly available data:
	spectral and spectro-morphological analyses, estimation of the light curve of a source.
	The flexibility and power of the software is displayed in a final multi-instrument example,
	where data sets from different instruments, at different stages of data reduction,
	are simultaneously fitted with a flux model produced by another astrophysical software.
}
